\documentclass[letterpaper,12pt]{article}
\usepackage[official]{eurosym}
\author{George Cummings}
\title{\LaTeX Quick Reference Card}
\begin{document}
\pagenumbering{roman}
\maketitle
\tableofcontents
\clearpage
\pagenumbering{arabic}
\section{Paragraphs}
\subsection{Paragraph Example 1}
\ldots when Einstein introduced his formula
\begin{equation}
	e = m \cdot c^2 \; ,
\end{equation}
which is at the same time the most widely known and the
least well understood physical formula. 
\subsection{Paragraph Example 2}
\ldots from which follows Kirchhoff's current law:
\begin{equation}
	\sum_{k=1}^{n} I_k = 0 \; .
\end{equation}

Kirchhoff's voltage law can be derived \ldots
\subsection{MBoxes}
MBoxes ensure that a block of text remains on the same line. For example,
the telephone number here is wrapped in an\verb| \mbox{}|: \mbox{(450) 330-4742}. 
\subsection{Ready-Made Strings}
\textbackslash today = \today \\
\textbackslash TeX = \TeX \\
\textbackslash LaTeX = \LaTeX \\
\textbackslash LaTeXe = \LaTeXe \\
\section{Special Characters and Symbols}
\subsection{Quotation Marks}
\`{}\`{}Please press the \`{}any\'{} key. \'{}\'{} = ``Please press the `any' key.''
\subsection{Dashes and Hyphens}
daughter-in-law, X-rated = daughter-in-law, X-rated (hyphen)\\
pages 13 - - 67 = pages 13--67 (en-dash)\\
yes - - - or no? = yes---or no? (em-dash)\\
\$0\$, \$1\$ and \$-1\$ = $0$, $1$ and $-1$ (minus) 
\subsection{Tilde}
\textbackslash\~{}\{\} gives a regular tilde: \~{} \\
For the web, use \$\textbackslash sim\$: http://cummings-online.ca/$\sim$george
\subsection{Slash between words}
read\textbackslash slash write = read\slash write
\subsection{Euros}
\textbackslash usepackage[official]\{eurosym\} \\
\textbackslash euro = \euro
\subsection{Ellipsis}
\textbackslash ldots = \ldots
\subsection{Suppress Ligatures}
ff, fi, fl, ffi: use f\textbackslash mbox\{\}l to get f\mbox{}l.
\section{References}
\subsection{Cross References}
\subsubsection{Target}
Use \textbackslash label\{\emph{identifier}\}. For example, a reference to this \label{examplelabel}
subsection uses \textbackslash label\{examplelabel\}.
\subsubsection{Cross Reference}
Now we can refer to the previous target with \textbackslash ref\{examplelabel\} on page
\textbackslash pageref\{examplelabel\}. For example, section \ref{examplelabel} on page
\pageref{examplelabel}.
\subsection{Footnotes}
Really easy. Just append \textbackslash footer\{\emph{Reference Text}\} to the word being referred to. For example,
``Foxes are not elephants''\footnote{Theodore Seuss, \emph{Horton Hears a Who}, p.12}.
\section{Environments}
\subsection{Verbatim}
This would be important for programming, I suppose. \\
\verb|\begin{verbatim}| \ldots \verb|\end{verbatim}| \\
Example: \\
\begin{verbatim}
import os

for i in 'thing whump fweep'.split():
    with open(os.path.join(CURDIR, i), 'r') as fp:
        fp.read()
\end{verbatim}
% Appendices --------------------------------------------
\clearpage
\appendix
\section{Appendix Example}
This is an example appendix.
\end{document}